Analysis plan

### 2023-01-23 02. Design/MSG-P2312-Analysis Plan.rmd

Insert text here, and delete the gray prompt above when the document is final

@@

<!-- [Briefly state the primary and any secondary hypotheses to be tested. Aim for plain language. Statistical models and details of hypothesis tests will be covered later; the purpose here is to set the stage for the sections that follow.] -->

Insert text here, and delete the gray prompt above when the document is final

@@

Insert text here, and delete the gray prompt above when the document is final

>>>>

The U.S. General Services Administration’s FY 2022 Annual Evaluation Plan includes evaluation goals that involve The Future of Work projects and objectives. This initiative is part of an effort to right-size the federal real estate footprint. Specifically, this project will examine the effects of distributed, virtual, and asynchronous work with the goal of informing future changes to interior space planning and building operations. We will join GSA telework rates and facility occupancy patterns with GSA roster data and describe rates of telework and on site work across employment and personal demographics. We will also determine the rates at which teams work together onsite, remotely, or in a hybrid environment.

@@

This work will address the following research questions:
1. What are the rates of telework since the federal return-to-office transition?
2. Do telework behaviors match position category (e.g., onsite, offsite, etc.) in the roster?
3. At what rates to teams work together onsite vs. remotely?
4. Do the telework patterns of supervisors match the telework patterns of supervisees?

At this stage, our research questions are aimed at describing patterns of telework and federal building occupancy rather than estimating the impacts of telework.

@@
